Lineal regression with one variable and one parameter for the cost function

### 2016-06-26 LinearRegression/Documentation/OneParam/OneParam.tex
adding gradient decend plots

    \begin{tikzpicture}
        \begin{axis}[ xmin=0, xmax=5,
                      ymin=0, ymax=10,
                      grid=both
                    ]
            \addplot[color=red, only marks]
                coordinates{
                    (1,2)
                    (1.5,1)
                    (1.5,3)
                    (2,2)
                    (2.5,4)
                    (3,5)
                    (3,4)
                    (3.5,4.5)
                    (3.5,5.5)
                    (4,5)
                    (4,6.5)
                    (4.5,8)
                };
        \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
        \begin{axis}[ xmin=0, xmax=5,
                      ymin=0, ymax=10,
                    ]
            \addplot[color=blue]{1.5*x};

@@

    Now that we have seen the process, we are gonig to formalize a little bit
    the process. The first thing that we are going to do is define a varible as
    the number of elements in each set

    \begin{itemize}
        \item $m = number\_of\_elements$
    \end{itemize}

@@

    This equation has the following graphic

    \begin{figure}[h!]

        \centering
        \captionsetup{justification=centering}

        \begin{tikzpicture}
            \begin{axis}[
                            xlabel=$\theta$,
                            ylabel=$J(\theta)$,
                            xmin=-5, xmax=5,
                            ymin=0, ymax=10,
                        ]
                \addplot[mark=none, color=blue]{x^2};
            \end{axis}
        \end{tikzpicture}

        \caption{Cost function}
    \end{figure}

@@

    The objective of this function is to actualize the parameter $\theta$
    of the cost function J minimizing the error in each iteration, this
    is done by searching the path to the global minimum. The function
    that we are going to use is described bellow.\\

    The first thing to do is replace the function $J(\theta)$

>>>>

    \begin{tikzpicture}
        \begin{axis}[
                      title={Input points},
                      xlabel=$x$,
                      ylabel=$y$,
                      xmin=0, xmax=5,
                      ymin=0, ymax=10,
                      grid=both
                    ]
            \addplot[color=red, only marks]
                coordinates{
                    (1,2)
                    (1.5,1)
                    (1.5,3)
                    (2,2)
                    (2.5,4)
                    (3,5)
                    (3,4)
                    (3.5,4.5)
                    (3.5,5.5)
                    (4,5)
                    (4,6.5)
                    (4.5,8)
                };
        \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
        \begin{axis}[
                      title={Predictions},
                      xlabel=$h(x)$,
                      ylabel=$y$,
                      xmin=0, xmax=5,
                      ymin=0, ymax=10,
                    ]
            \addplot[color=blue]{1.5*x};

@@

    Now that we have seen the process, we are gonig to formalize a little bit
    the process. The first thing that we are going to do is define a varible as
    the number of elements in each set \\

    \begin{itemize}
        \item $m = number\_of\_elements$ \\
    \end{itemize}

@@

    This equation will have the following graphic

    \begin{figure}[h!]
        \begin{tikzpicture}
            \begin{axis}[
                         title={Cost function},
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=blue]{x^2};
            \end{axis}
        \end{tikzpicture}
    \end{figure}

@@

    The objective of this function is to actualize the parameter $\theta$
    of the cost function J minimizing the error in each iteration, this
    is done by searching the path to the global minimum. \\

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

                \draw[thick,->] (axis cs: 3.5,16) -- node[left]{$\alpha \Bigg(\frac{d}{d \theta} J(\theta)\Bigg)$} (axis cs: 2.65,9.75);
                \draw[thick,->] (axis cs: 2.5,9) -- (axis cs: 1.65,4.75);
                \draw[thick,->] (axis cs: 1.5,4) -- (axis cs: 0.75,2);
                \draw[thick,->] (axis cs: 0.75,1.75) -- (axis cs: 0,0.75);

                \addplot[color=blue, only marks]
                coordinates{
                    (4,16)
                    (3,9)
                    (2,4)
                    (1,1)
                    (0,0)
                };
            \end{axis}
        \end{tikzpicture}
    \end{figure}

    \begin{figure}[ht!]
        \begin{tikzpicture}
            \begin{axis}[
                         title={Gradient decend with negative derivative},
                         xlabel=$\theta$,
                         ylabel=$J(\theta)$,
                         ymin=0, ymax=25,
                         xtick=\empty,
                         ytick=\empty
                        ]
                \addplot[mark=none, color=red]{x^2};

                \draw[thick,->] (axis cs: -3.5,16) -- node[right]{$\alpha\Bigg(\frac{d}{d\theta}J(\theta)\Bigg)$} (axis cs: -2.65,9.75);
                \draw[thick,->] (axis cs: -2.5,9) -- (axis cs: -1.65,4.75);
                \draw[thick,->] (axis cs: -1.5,4) -- (axis cs: -0.75,2);
                \draw[thick,->] (axis cs: -0.75,1.75) -- (axis cs: -0,0.75);

                \addplot[color=blue, only marks]
                coordinates{
                    (-4,16)
                    (-3,9)
                    (-2,4)
                    (-1,1)
                    (0,0)
                };
            \end{axis}
        \end{tikzpicture}
    \end{figure}

    The function that we are going to use is described bellow. The first thing
    to do is replace the function $J(\theta)$
